Agile Inter-team Software Development

### 2019-01-20 Draft/Parts/Introduction.tex
Updated the introduction section to reflect new sections and updated the section 3 name to proposed approach

%outline of rest of paper
This document is separated into five sections: Introduction, Process Inprovements, Technology Improvements, Importance of Architecture \& Design, and Conclusion. 
In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication.
In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.

>>>>

%outline of rest of paper
This document is separated into four sections: Introduction, Sportify: A Canonical Example, Proposed Approach and Conclusion. 
In Section ~\ref{sec:spt_ex}, we discuss the a real world example of large scale agile project and show a problem encountered in that.
In Section ~\ref{sec:prop_appro}, we present some adaptations that can be done in agile process model to resolve the problem discussed.

### 2019-01-20 Draft/Parts/Main.tex
Updated the introduction section to reflect new sections and updated the section 3 name to proposed approach

\section{Spotify: A Canonical Example} 
For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of the development organization at Spotify is the Squad, analogous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes. 
The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

@@

\section{NAME ME} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.

>>>>

\section{Spotify: A Canonical Example} 
\label{sec:spt_ex} 
For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of the development organization at Spotify is the Squad, analogous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes. 
The overall structure is illustrated in Figure~\ref{fig:spotify_structure}.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

@@

\section{Proposed Approach}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.
